Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-06-01 tex/test-WW-type-00v-PS.tex
alexei

\author[a]{S.~Bastami}
\author[b]{H.~Avakian}
\author[c]{A.~V.~Efremov} 
\author[d,e]{A.~Kotzinian} 
\author[f]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[g,b]{A.~Prokudin} 
\author[h]{M.~Schlegel} 
\author[i]{G.~Schnell} 
\author[a,j]{P.~Schweitzer} 
\author[a]{K.~Tezgin}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[c]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[d]{Yerevan Physics Institute,  Alikhanyan Brothers St.,
	375036 Yerevan, Armenia}
\affiliation[e]{INFN, Sezione di Torino, 
	10125 Torino, Italy}
\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[g]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[h]{Department of Physics, New Mexico State University, 
	Las Cruces, NM 88003-001, USA}
\affiliation[i]{Department of Theoretical Physics, University of the Basque 
	Country UPV/EHU, 48080 Bilbao, Spain, and
	IKERBASQUE, Basque Foundation for Science, 48013 Bilbao, Spain}
\affiliation[j]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	D-72076 T\"ubingen, Germany} % Auf der Morgenstelle 14,

@@

The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the
consistent result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in 
WW-type approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction 
is therefore $A_{UT}^{\sin\phi_S}(x)=F_{UT}^{\sin\phi_S}(x)/F_{UU}(x)=0$.
This is compatible with preliminary data from HERMES \cite{Schnell:2010zza}
and COMPASS \cite{Parsamyan:2015dfa} over a wide range of $x$, see 
Fig.~\ref{autsinphi_jlab} below. Merely for negative hadrons at 
large-$x$ there might be a disagreement with our prediction.

>>>>

\author[a]{S.~Bastami}
\author[b]{H.~Avakian}
\author[c]{A.~V.~Efremov} 
\author[d,e]{A.~Kotzinian} 
\author[f]{B.~U.~Musch} 
\author[k]{B.~Parsamyan} 
\author[g,b]{A.~Prokudin} 
\author[h]{M.~Schlegel} 
\author[i]{G.~Schnell} 
\author[a,j]{P.~Schweitzer} 
\author[a]{K.~Tezgin}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[c]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[d]{Yerevan Physics Institute,  Alikhanyan Brothers St.,
	375036 Yerevan, Armenia}
\affiliation[e]{INFN, Sezione di Torino, 
	10125 Torino, Italy}
\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[g]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[k]{CERN, 1211 Geneva 23, Switzerland}
\affiliation[h]{Department of Physics, New Mexico State University, 
	Las Cruces, NM 88003-001, USA}
\affiliation[i]{Department of Theoretical Physics, University of the Basque 
	Country UPV/EHU, 48080 Bilbao, Spain, and
	IKERBASQUE, Basque Foundation for Science, 48013 Bilbao, Spain}
\affiliation[j]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	D-72076 T\"ubingen, Germany} % Auf der Morgenstelle 14,

@@

The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the
consistent result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in 
WW-type approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction 
is therefore $A_{UT}^{\sin\phi_S}(x)=F_{UT}^{\sin\phi_S}(x)/F_{UU}(x)=0$.
{\color{green} Even though this is compatible with preliminary data from HERMES \cite{Schnell:2010zza}
and COMPASS \cite{Parsamyan:2015dfa} over a wide range of $x$, see 
Fig.~\ref{autsinphi_jlab} below, one must notice that for negative hadrons at 
large-$x$ there is a disagreement with our prediction.

In fact at this point we should notice that WW approximation has its limitations, especially for the case of $A_{UT}^{\sin\phi_S}(x)$ one would expect that this asymmetry is sensitive to $\tilde H$ (which we neglect in this approximation):
\begin{equation}
F_{UT}^{\sin\phi_S}(x,z) 
	= -x \,\frac{2m_h}{Q}\;\sum_q e_q^2\,
	h_1^{q}(x)\; \frac{\tilde H_1^{q}(z)}{z} 
\end{equation}	
As pointed out in Ref.~\cite{Kanazawa:2015ajw}, both $H_1^{\perp(1)q}$ and $\tilde H_1^{q}$ are related to integrals of underlying function $H_{FU}^{q,\Im}(z,z_1)$ and thus, strictly  speaking, neglecting $\tilde H_1^{q}$ would mean neglecting  $H_1^{\perp(1)q}$ as well. Thus, particularly in the fragmentation sector WW-type approximation has serious limitations.}
